A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-02-18 paper/paper.Rmd
nice paragraph on gender and race

It is worth noting that `gender` comes from a variable called `sex` in the database. We use the term `gender` as the reports on the data on the website typically use `gender`. Gender, as provided in the data, is self-reported and only has two categories, "male" and "female". The interchangeable use of these terms reflects that gender and sex are sometimes regarded as similar in surveys, although they are not. Measuring gender as a binary variable has the potential to fail to capture people who do not identify themself as either male or female or people whose gender does not align with their sex classification [@kennedy2020using]. From a statistical perspective, this sometimes difficult the adjustment of survey statistics to the population when gender is measured, for example, with three categories, and the census measured it with only two categories and used the term sex [@kennedy2020using]. Hence, nowadays, it is highly recommended to separate sex and gender in the survey question and provide more options to respond to questions on gender. This discourse should also be emphasized in teaching that using these two variables should be accompanied by special attention. Similar case to race, as reported in the database. When doing an analysis with this variable, one should keep in mind that the purpose is to study racism rather than race.

>>>>

It is worth noting that `gender` comes from a variable called `sex` in the database. We use the term `gender` as the reports about the data on various pages in the website more commnly use `gender`. Gender, as provided in the data, is self-reported and only has two categories, "male" and "female". The interchangeable use of these terms reflects that gender and sex are sometimes regarded as similar in surveys, although they are not. Measuring gender as a binary variable has the potential to fail to capture people who do not identify themselves as either male or female or people whose gender does not align with their sex classification [@kennedy2020using]. From a statistical perspective, this sometimes difficult the adjustment of survey statistics to the population when gender is measured, for example, with three categories, and the census measured it with only two categories and used the term sex [@kennedy2020using]. Hence, for modern societal studies, it is highly recommended to separate sex and gender in the survey question and provide more options to respond to questions on gender. This discourse should also be emphasized in teaching that using these two variables should be accompanied by special attention. Similar this also relates to race, as reported in the database. When doing an analysis with this variable, one should keep in mind that the purpose is to study racism rather than race.

### 2022-02-18 paper/paper.tex
nice paragraph on gender and race

It is important to discuss the two variables gender and race. Gender comes from the variable called sex in the database, but the reports on the data on the web site typically use gender. Using these two variables should be accompanied with special attention. Gender, as provided in the data, if self-reported. It only has two categories, which is recognised today as inadequate. Gender is not binary, and this needs to be emphasized in teaching. Further, race is as reported in the database. When doing analysis with this variable, one should keep in mind that the purpose is to study racism rather than race.

@@

>>>>

It is worth noting that \texttt{gender} comes from a variable called \texttt{sex} in the database. We use the term \texttt{gender} as the reports about the data on various pages in the website more commnly use \texttt{gender}. Gender, as provided in the data, is self-reported and only has two categories, ``male'' and ``female''. The interchangeable use of these terms reflects that gender and sex are sometimes regarded as similar in surveys, although they are not. Measuring gender as a binary variable has the potential to fail to capture people who do not identify themselves as either male or female or people whose gender does not align with their sex classification (Kennedy et al. 2020). From a statistical perspective, this sometimes difficult the adjustment of survey statistics to the population when gender is measured, for example, with three categories, and the census measured it with only two categories and used the term sex (Kennedy et al. 2020). Hence, for modern societal studies, it is highly recommended to separate sex and gender in the survey question and provide more options to respond to questions on gender. This discourse should also be emphasized in teaching that using these two variables should be accompanied by special attention. Similar this also relates to race, as reported in the database. When doing an analysis with this variable, one should keep in mind that the purpose is to study racism rather than race.

@@

\leavevmode\vadjust pre{\hypertarget{ref-kennedy2020using}{}}%
Kennedy, Lauren, Katharine Khanna, Daniel Simpson, and Andrew Gelman. 2020. {``Using Sex and Gender in Survey Adjustment.''} \url{https://arxiv.org/abs/2009.14401}.
